Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
content additions largely complete, editing time

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and have seen multiple extensions over the years.  Although
it's pretty certain that extensions to these languages that are published are
correct, errors to creep into even the most scrutinized of paper results (as we
have observed in this project), and so requiring these extensions to come with
mechanized proofs of correctness before incorporation into a verified compiler
would help ensure that the language updates will not invalidate pre-existing
security properties of the language.

>>>>

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and have seen multiple extensions over the years.  Although
it's pretty certain extensions to these languages that are published are
correct, errors to creep into even the most scrutinized of paper results (as we have observed in this project), and so requiring these extensions to come with mechanized proofs of correctness before incorporation into a verified compiler would
help ensure that the language updates will not invalidate pre-existing security
properties of the language.
